---
institute: "OverDrive"
output: 
  xaringan::moon_reader:
    seal: FALSE
    includes: 
      after_body: insert-logo.html
    lib_dir: libs
    # yolo: true
    css: ["default", "./my-theme2.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

layout: true

<div class="my-footer"><span> OverDrive Confidential: Internal Use Only
</span></div> 

---

class: center, middle


<br />
 <span style="color:white"> <font size="9">**Lead Activities Analysis**</span></font>
 <br />
 <span style="color:white"> <font size="6">** **</span></font>
 <br />
<font size="5">
August 8, 2022
</font>
<br />
<font size="5">
Hao Feng
</font>
<br />
<font size="5">
Business Systems & Analytics
</font>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA)
knitr::opts_knit$set(root.dir = "C:/teporaryFiles/indi")
options(scipen = 999)
options(cache = TRUE)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
require(ggplot2); require(tidyr); library(plyr); require(dplyr); require(RODBC); require(kableExtra); require(pander); require(lubridate); require(cowplot); require(data.table); require(knitr);  require(gridExtra); require(openxlsx); require(scales);
require(wordcloud); require(tm); require(rpart); require(rpart.plot)

```



```{r echo=FALSE}
cn1 <- odbcDriverConnect('driver={SQL Server};server=reportDB;database=master;trusted_connection=true')
```




```{r echo=FALSE}

# #cs1 <- sqlQuery(cn,
# #                         paste("
# 
# #DECLARE 
# # @CRID INT --= 612
# #, @StartDate DATE = '03-01-2022'
# #, --@EndDate DATE = GETDATE() --GETDATE() = Today
# #   @EndDate DATE = '06-01-2022' --GETDATE() = Today
# 
# #--Delete purchases if it exists
# #IF OBJECT_ID('tempdb.dbo.#purchases') IS NOT NULL
# 	DROP TABLE #purchases
# 
# --purchase orders
# SELECT
# 	dcc.CR_ID_INT__c AS CRID
# 	, [Purchase Type] = 'Purchase Orders'
# 	--,[Year] = YEAR(lpor.lporActualAddDate)
# 	,[Platform] = dcc.Platform_Type__c
# 	,SpendUSD = SUM(lpod.lpodTotalPriceUSD)
# 	,CAST(lpor.lporActualAddDate AS DATE) AS DayDate
# INTO #purchases
# FROM contentReserve.dbo.LibraryPurchaseOrder lpor
# INNER JOIN contentReserve.dbo.LibraryPurchaseOrderDetail lpod
# 	ON lpor.lporPORecordID = lpod.lporPORecordID
# --INNER JOIN #titles t
# --	ON lpod.coinCrossRefID = t.CrossRefID
# INNER JOIN sf_mirror.dbo.Digital_Collection__c dcc
# 	ON lpor.acacAccessID = dcc.CR_ID_INT__c
# WHERE
# 	--YEAR(lpor.lporActualAddDate) BETWEEN 2018 AND 2021
# 	CAST(lpor.lporActualAddDate AS DATE) BETWEEN @StartDate AND @EndDate
# 	--AND dcc.Platform_Type__c IN ('DLR','CDL')
# 	--AND dcc.CR_ID_INT__c=@CRID
# GROUP BY
# 	dcc.CR_ID_INT__c
# 	,CAST(lpor.lporActualAddDate AS DATE)
# 	,dcc.Platform_Type__c
# 
# UNION
# 
# --subscriptions
# SELECT
# 	dcc.CR_ID_INT__c AS CRID
# 	, [Purchase Type] = 'Subscriptions'
# 	--,[Year] = YEAR(psl.psliActualAddDate)
# 	,[Platform] = dcc.Platform_Type__c	
# 	,SpendUSD = SUM(ROUND(psl.psliSubscriptionCost * ((100 - psdiDiscount) / 100), 2)/ sc.Units)
# 	,CAST(psl.psliActualAddDate AS DATE) AS DayDate
# FROM contentReserve.dbo.PublisherSubscriptionLibrary psl
# INNER JOIN
# (
# 	SELECT	
# 		Units = COUNT(1)
# 		,psl.psliPublisherSubscriptionLibraryID
# 	FROM contentReserve.dbo.PublisherSubscriptionLibrary psl
# 	INNER JOIN contentReserve.dbo.PublisherSubscriptionLibraryTitle pslt
# 		ON psl.psliPublisherSubscriptionLibraryID = pslt.psliPublisherSubscriptionLibraryID
# 	GROUP BY
# 		psl.psliPublisherSubscriptionLibraryID
# )sc
# 	ON psl.psliPublisherSubscriptionLibraryID = sc.psliPublisherSubscriptionLibraryID
# INNER JOIN contentReserve.dbo.PublisherSubscriptionLibraryTitle pslt
# 	ON psl.psliPublisherSubscriptionLibraryID = pslt.psliPublisherSubscriptionLibraryID
# --INNER JOIN #titles t
# --	ON pslt.coinCrossRefID = t.CrossRefID
# INNER JOIN contentReserve.dbo.ListPurchaseOrderType lpot
# 	ON psl.lpotTypeID = lpot.lpotTypeID
# INNER JOIN sf_mirror.dbo.Digital_Collection__c dcc
# 	ON psl.acacAccessID = dcc.CR_ID_INT__c
# WHERE
# 	CAST(psl.psliActualAddDate AS DATE) BETWEEN @StartDate AND @EndDate
# 	--AND dcc.CR_ID_INT__c=@CRID
# GROUP BY
# 	dcc.CR_ID_INT__c
# 	,CAST(psl.psliActualAddDate AS DATE)
# 	,dcc.Platform_Type__c
# 
# UNION
# 
# --CPC
# SELECT
# 	dcc.CR_ID_INT__c AS CRID
# 	,[Purchase Type] = 'CPC'
# 	--,[Year] = YEAR(udl.udloDownloadLogDate)
# 	,[Platform] = dcc.Platform_Type__c
# 	,SpendUSD = SUM(udlf.udlfSrpAmountUSD)
# 	,CAST(udl.udloDownloadLogDate AS DATE) AS DayDate
# FROM contentReserve.dbo.UniqueDownloadLog udl
# INNER JOIN contentReserve.dbo.UniqueDownloadLogFinance udlf
# 	ON udl.udloDownloadID = udlf.udloDownloadID
# INNER JOIN contentReserve.dbo.UniqueDownloadLogPerCirc udlpc
# 	ON udl.udloDownloadID = udlpc.udloDownloadID
# --INNER JOIN #titles t
# --	ON udl.coinCrossRefID = t.CrossRefID
# INNER JOIN sf_mirror.dbo.Digital_Collection__c dcc
# 	ON udl.acacAccessIDRetailer = dcc.CR_ID_INT__c
# WHERE
# 	CAST(udl.udloDownloadLogDate AS DATE) BETWEEN @StartDate AND @EndDate
# 	-- AND dcc.CR_ID_INT__c = @CRID
# GROUP BY
# 	dcc.CR_ID_INT__c
# 	,CAST(udl.udloDownloadLogDate AS DATE)
# 	,dcc.Platform_Type__c
# 
# UNION
# 
# -- adjustments
# SELECT
# 	dcc.CR_ID_INT__c AS CRID
# 	,[Purchase Type] = 'Adjustments'
# 	--,[Year] = YEAR(lpoda.lpodaAdjustmentDate)
# 	,[Platform] = dcc.Platform_Type__c
# 	,SpendUSD = -SUM(lpod.lpodTotalPriceUSD)
# 	,CAST(lpoda.lpodaAdjustmentDate AS DATE) AS DayDate
# FROM contentReserve.dbo.LibraryPurchaseOrder lpo
# INNER JOIN contentReserve.dbo.LibraryPurchaseOrderDetail lpod
# 	ON lpo.lporPORecordID = lpod.lporPORecordID
# INNER JOIN contentReserve.dbo.LibraryPurchaseOrderDetailAdjustment lpoda
# 	ON lpo.lporPORecordID = lpoda.lporPORecordID
# 	AND lpod.coinReserveID = lpoda.coinReserveID
# 	AND lpo.acacAccessID = lpoda.acacAccessID
# --INNER JOIN #titles t
# --	ON lpod.coinCrossRefID = t.CrossRefID
# INNER JOIN sf_mirror.dbo.Digital_Collection__c dcc
# 	ON lpo.acacAccessID = dcc.CR_ID_INT__c
# WHERE
# 	CAST(lpoda.lpodaAdjustmentDate AS DATE) BETWEEN @StartDate AND @EndDate
# 	--AND dcc.CR_ID_INT__c=@CRID
# GROUP BY
# 	dcc.CR_ID_INT__c
# 	,CAST(lpoda.lpodaAdjustmentDate AS DATE)
# 	,dcc.Platform_Type__c
# 
# 
# 
# 
# select *
# from #purchases
# --If all days needed for analysis/visuals, use dw.dbo.DimDate2 for scaffolding (aka use dimdate and left outer join to purchases based on date)!!
# 
# 
# 
# 
# 
# 
# --Use to 'flatten' data to CRID/Date
# SELECT CRID
# , P.DayDate
# , p.[Platform]
# , COALESCE(SUM(CASE WHEN [Purchase Type] = 'Adjustments' THEN SpendUSD END),0) AS [Adjustments]
# , COALESCE(SUM(CASE WHEN [Purchase Type] = 'CPC' THEN SpendUSD END),0) AS [CPC]
# , COALESCE(SUM(CASE WHEN [Purchase Type] = 'Subscriptions' THEN SpendUSD END),0) AS [Subscriptions]
# , COALESCE(SUM(CASE WHEN [Purchase Type] = 'Purchase Orders' THEN SpendUSD END),0) AS [PurchaseOrders]
# , COALESCE(SUM(SpendUSD),0) AS [TotalSpend]
# 
# INTO #spend
# FROM 
# #purchases p
# GROUP BY p.DayDate
# 	,CRID
# 	, p.[Platform]
# ORDER BY p.DayDate
# 	,CRID
# 
# 
# 
# select #spend.* ,
# dc.Subscription_Tier__c,
# dc.Region__c,
# dc.Subregion__c,
# dc.Days_Live__c
# from
# #spend
# left join sf_mirror.dbo.Digital_Collection__c dc on dc.CR_ID__c = #spend.CRID
# Order by DayDate 
# 
# " ))
```


```{r echo=FALSE}

#setwd('C:/teporaryFiles/indi')

#cs1 <- read.csv('indi1.csv')

#cs1


```



```{r echo=FALSE}
#cs2 <- cs1 %>% group_by(Platform, Date = as.Date(DayDate, "%m/%d/%Y")) %>% dplyr::summarise(TotalSpend=sum(TotalSpend), #TotalCPC=sum(CPC), TotalSubs=sum(Subscriptions), TotalPurchase=sum(PurchaseOrders))

#cs2
```


```{r echo=FALSE}
#cs3 <- cs2 %>% group_by(Platform) %>% dplyr::summarise(TotalSpend=sum(TotalSpend), TotalCPC=sum(TotalCPC), #TotalSubs=sum(TotalSubs), TotalPurchase=sum(TotalPurchase))

#cs3


#ggplot(cs3, aes_string(x = "Platform", y="TotalSpend")) + 
#   geom_bar(position="stack",stat="identity") +
#   geom_line(aes(x= "Platform", y="TotalCPC"))+
#   geom_line(aes(x="Platform", y="TotalSubs"))
# +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + scale_x_date(date_breaks = "1 year", date_labels =  "%Y")  + labs( y = "Checkouts", x = "Date")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")
```


```{r  echo=FALSE}
```


```{r echo=FALSE}
# ggplot(cs3) + 
#   geom_col(aes(x = Platform, y = TotalSpend), size = 1, color = "darkblue", fill = "white") +
#   geom_line(aes(x = Platform, y = TotalCPC), size = 1.5, color="red", group = 1) + 
#   geom_line(aes(x = Platform, y = TotalSubs), size = 1.5, color="black", group = 1) + 
#   geom_line(aes(x= Platform, y = TotalPurchase), size = 1.5, color="yellow", group = 1)
```


```{r echo=FALSE}

# ggplot(cs2 %>% filter(Platform %in% c("DLR","SDL")),aes(x=Date,y=)) + 
#   geom_line(aes(group = CRID))+ geom_smooth(aes(group = 1/5), size = 1, method = "loess", color = "black") + 
#   guides(colour=FALSE)+ facet_wrap(~ as.factor(Platform),scales = "free_x") +
#   theme(text = element_text(size=16)) +
#   labs(x = "Year Since Live",y = "Total Value",title= "Total Cumulative Value Over Lifetime",subtitle="DLR vs. SDL") +
#   theme_grey()+ scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16),minor_breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16))

```





---
## Purpose: 
* Which channel/source/industry generate more leads
* What factors impact on the leads converted or not 
* Help the marketing team better targeting customers and campaigning 



```{r echo=FALSE, message=FALSE, warning=FALSE}
cn <- odbcDriverConnect('driver={SQL Server};server=reportDB;database=sf_mirror;trusted_connection=true')

Q3_2021 <- sqlQuery(cn,
                         paste("
select
Background_Notes__c,
Country,
Industry,
--CreatedById
CAST (CreatedDate AS DATE) as CreatedDate,
CAST (ConvertedDate AS DATE) as ConvertedDate,
DATEDIFF(DAY, CAST(CreatedDate AS DATE) , CAST(ConvertedDate AS DATE)) as ConvertTime,
Data_Quality_Description__c,
Data_Quality_Score__c,
LeadSource,
Source__c,
Status,
IsConverted,
IsUnreadByOwner,
IsDeleted
from sf_mirror.dbo.lead
where CreatedDate >= CONVERT(datetime, '2021-07-01')
  and CreatedDate < CONVERT(datetime, '2021-09-30')
"))


Q1_2021 <- sqlQuery(cn,
                         paste("
select
Background_Notes__c,
Country,
Industry,
--CreatedById
CAST (CreatedDate AS DATE) as CreatedDate,
CAST (ConvertedDate AS DATE) as ConvertedDate,
DATEDIFF(DAY, CAST(CreatedDate AS DATE) , CAST(ConvertedDate AS DATE)) as ConvertTime,
Data_Quality_Description__c,
Data_Quality_Score__c,
LeadSource,
Source__c,
Status,
IsConverted,
IsUnreadByOwner,
IsDeleted
from sf_mirror.dbo.lead
where CreatedDate >= CONVERT(datetime, '2021-01-01')
  and CreatedDate < CONVERT(datetime, '2021-03-30')
"))


Q3_2020 <- sqlQuery(cn,
                         paste("
select
Background_Notes__c,
Country,
Industry,
--CreatedById
CAST (CreatedDate AS DATE) as CreatedDate,
CAST (ConvertedDate AS DATE) as ConvertedDate,
DATEDIFF(DAY, CAST(CreatedDate AS DATE) , CAST(ConvertedDate AS DATE)) as ConvertTime,
Data_Quality_Description__c,
Data_Quality_Score__c,
LeadSource,
Source__c,
Status,
IsConverted,
IsUnreadByOwner,
IsDeleted
from sf_mirror.dbo.lead
where CreatedDate >= CONVERT(datetime, '2020-07-01')
  and CreatedDate < CONVERT(datetime, '2020-09-30')
"))



Q1_2020 <- sqlQuery(cn,
                         paste("
select
Background_Notes__c,
Country,
Industry,
--CreatedById
CAST (CreatedDate AS DATE) as CreatedDate,
CAST (ConvertedDate AS DATE) as ConvertedDate,
DATEDIFF(DAY, CAST(CreatedDate AS DATE) , CAST(ConvertedDate AS DATE)) as ConvertTime,
Data_Quality_Description__c,
Data_Quality_Score__c,
LeadSource,
Source__c,
Status,
IsConverted,
IsUnreadByOwner,
IsDeleted
from sf_mirror.dbo.lead
where CreatedDate >= CONVERT(datetime, '2020-01-01')
  and CreatedDate < CONVERT(datetime, '2020-03-30')
"))


Q3_2019 <- sqlQuery(cn,
                         paste("
select
Background_Notes__c,
Country,
Industry,
--CreatedById
CAST (CreatedDate AS DATE) as CreatedDate,
CAST (ConvertedDate AS DATE) as ConvertedDate,
DATEDIFF(DAY, CAST(CreatedDate AS DATE) , CAST(ConvertedDate AS DATE)) as ConvertTime,
Data_Quality_Description__c,
Data_Quality_Score__c,
LeadSource,
Source__c,
Status,
IsConverted,
IsUnreadByOwner,
IsDeleted
from sf_mirror.dbo.lead
where CreatedDate >= CONVERT(datetime, '2019-07-01')
  and CreatedDate < CONVERT(datetime, '2019-09-30')
"))


Q1_2019 <- sqlQuery(cn,
                         paste("
select
Background_Notes__c,
Country,
Industry,
--CreatedById
CAST (CreatedDate AS DATE) as CreatedDate,
CAST (ConvertedDate AS DATE) as ConvertedDate,
DATEDIFF(DAY, CAST(CreatedDate AS DATE) , CAST(ConvertedDate AS DATE)) as ConvertTime,
Data_Quality_Description__c,
Data_Quality_Score__c,
LeadSource,
Source__c,
Status,
IsConverted,
IsUnreadByOwner,
IsDeleted
from sf_mirror.dbo.lead
where CreatedDate >= CONVERT(datetime, '2019-01-01')
  and CreatedDate < CONVERT(datetime, '2019-03-30')
"))

```




```{r}
#### which channel/source/industry usually generate more leads
#### what factors impact on the leads converted or not 

Q3_2021$cohort <- "2021Q3"

Q1_2021$cohort <- "2021Q1"

Q3_2020$cohort <- "2020Q3"

Q1_2020$cohort <- "2020Q1"

Q3_2019$cohort <- "2019Q3"

Q1_2019$cohort <- "2019Q1"

df_total <- rbind(Q3_2021, Q1_2021, Q3_2020, Q1_2020, Q3_2019, Q1_2019)


df_total$Industry <- ifelse (df_total$Industry == "Library", "Library", ifelse(df_total$Industry == "K-12 Education" ,"K-12 Education", ifelse(df_total$Industry == "Higher Education", "Higher Education", ifelse(df_total$Industry == "Other", "Other", "Profession"))))

#df_total

```

---
# Total Leads
* Total Leads from 2019-2021 Q1 & Q3
* 2020 Q3: School start year, begins remotely study


```{r fig.height=5, fig.width=12}
#### which channel/source/industry usually generate more leads
#### what factor impacts on the leads converted or not  

df_total1 <- df_total %>% group_by(cohort) %>% count(cohort)

#df_total1

ggplot(df_total1, aes(x = cohort, y = n)) +
  geom_col(aes(group = 1), color = "black", fill = "#507f94") +
  #geom_smooth(formula = y ~ x , method = "lm", color = "#507f94", se = FALSE, size = 1.5) +
  theme_classic()  +
  #geom_text(size = 5.5, fontface = "bold") +
  xlab("Time") +
  ylab("Total Leads") +
  theme(axis.text = element_text(size = 14), axis.title = element_text(size = 16)) 


```

---
# Total Leads --- Industry
* K-12 is highest, especially 2020-Q3

```{r echo=FALSE, fig.height=5, fig.width=12}

df_total2 <- df_total %>% group_by(cohort, Industry) %>% count(cohort)

#df_total2

ggplot(df_total2, aes(x = cohort, y = n, fill = Industry)) +
  geom_col(aes(group = 1), color = "black") +
  #geom_smooth(formula = y ~ x , method = "lm", color = "#507f94", se = FALSE, size = 1.5) +
  theme_classic()  +
  #geom_text(size = 5.5, fontface = "bold") +
  xlab("Time") +
  ylab("Total Leads") +
  theme(axis.text = element_text(size = 14), axis.title = element_text(size = 16)) 
```


---
# Total Leads Sources
* Most K-12 leads come from sora related activities 

```{r echo=FALSE, fig.height=4, fig.width=13}

df_total3 <- df_total %>% group_by(cohort, LeadSource) %>% count(cohort)

#df_total3

ggplot(df_total3, aes(x = cohort, y = n, fill = LeadSource)) +
  geom_col(aes(group = 1), color = "black") +
  #geom_smooth(formula = y ~ x , method = "lm", color = "#507f94", se = FALSE, size = 1.5) +
  theme_classic()  +
  #geom_text(size = 5.5, fontface = "bold") +
  xlab("Time") +
  ylab("Total Leads") +
  theme(axis.text = element_text(size = 14), axis.title = element_text(size = 16))



```


---
# Converted or Not
* Stable around 0.75 


```{r echo=FALSE, fig.height=5, fig.width=12}

###convention rate

df_cont1 <- df_total %>% group_by(cohort) %>% summarise(ConventionRate = sum(IsConverted)/ (sum(IsConverted) + sum(IsDeleted) + sum(IsUnreadByOwner)))

ggplot(df_cont1, aes(x = cohort, y = ConventionRate)) +
  geom_col(aes(group = 1), color = "black", fill = "#507f94") +
  #geom_smooth(formula = y ~ x , method = "lm", color = "#507f94", se = FALSE, size = 1.5) +
  theme_classic()  +
  #geom_text(size = 5.5, fontface = "bold") +
  xlab("Cohort") +
  ylab("Convention Rate") +
  theme(axis.text = element_text(size = 14), axis.title = element_text(size = 16)) 

```


```{r echo=FALSE}
##compare convented and non-convented difference

df_total$LeadSource <- ifelse(df_total$LeadSource %like% "Web", "Web", ifelse(df_total$LeadSource %like% "Trade", "Trade Show", ifelse(df_total$LeadSource %like% "Sora", "Sora", ifelse(df_total$LeadSource %like% "Form", "Form", ifelse(df_total$LeadSource %like% "Card", "Card",ifelse(df_total$LeadSource %like% "Onboarding", "Onboarding", "other"))))))


df_cont2 <- df_total[df_total$IsConverted == 1, ]

#df_cont2

df_cont3 <- df_total[df_total$IsConverted != 1, ]


```


---
# Compare Convertion Situation based on LeadSource
* Converted-- Sora, Web, Trade Show Perform well


```{r echo=FALSE, fig.height=5, fig.width=12}
df_cont2_1 <- df_cont2 %>% dplyr::group_by(LeadSource) %>% dplyr::count(cohort)

df_cont3_1 <- df_cont3 %>% dplyr::group_by(LeadSource) %>% dplyr::count(cohort)
#only2021_2

ggplot(na.omit(df_cont2_1), aes(x=cohort, y=n, fill = LeadSource)) +
geom_col(aes(group = 1), color = "black") +
theme(legend.title= element_blank()) + labs( y = "Converted Volumn", x = "Cohort")


```

---
# Compare Convertion Situation based on LeadSource
* Non-Convered: Web, no Trade show


```{r}

ggplot(na.omit(df_cont3_1), aes(x=cohort, y=n, fill = LeadSource)) +
geom_col(aes(group = 1), color = "black") +
  theme(legend.title= element_blank()) + labs( y = "Non-Converted Volumn", x = "Cohort")

```


---
# Compare Convertion Situation based on Industry
* Non-Convered: Web, no Trade show

```{r}

df_cont2_2 <- df_cont2 %>% group_by(Industry) %>% dplyr::count(cohort)
#df_cont2_2
df_cont3_2 <- df_cont3 %>% group_by(Industry) %>% dplyr::count(cohort)
#only2021_2

cont2_2<- ggplot(na.omit(df_cont2_2), aes(x=cohort, y=n, fill = Industry)) +
geom_col(aes(group = 1), color = "black")

cont3_2 <- ggplot(na.omit(df_cont3_2), aes(x=cohort, y=n, fill = Industry)) +
geom_col(aes(group = 1), color = "black")



```

---
# Compare Convertion Situation based on Industry
* Non-Convered: Web, no Trade show

```{r echo=FALSE, fig.height=6, fig.width=12}
####converted 

df_total_1 <- df_total %>% group_by(Industry, Converted = as.factor(IsConverted)) %>% dplyr::count(as.factor(IsConverted))
#df_total_1

ggplot(df_total_1, aes(x= Converted, y=n, fill = Industry)) +
geom_col(aes(group = 1), color = "black")

```

---
# Compare Convertion Situation based on LeadSource

```{r echo=FALSE, fig.height=5, fig.width=12}

df_total_2 <- df_total %>% group_by(LeadSource, Converted = as.factor(IsConverted)) %>% dplyr::count(as.factor(IsConverted))

ggplot(df_total_2, aes(x= Converted, y=n, fill = LeadSource)) +
geom_col(aes(group = 1), color = "black")




```


---
# Compare Convertion Situation based on Data Quality 

```{r echo=FALSE, fig.height=5, fig.width=12, message=FALSE, warning=FALSE}

df_total_3 <- df_total %>% group_by(Data_Quality_Description__c , Converted = as.factor(IsConverted)) %>%  dplyr::count(as.factor(IsConverted))

#df_total_3

ggplot(df_total_3, aes(x= Converted, y=n, fill = Data_Quality_Description__c)) +
geom_col(aes(group = 1), color = "black")




```

---
# Compare Convertion Situation based on Data Quality 

```{r echo=FALSE, fig.height=5, fig.width=12, message=FALSE, warning=FALSE}

ggplot(df_total_3, aes(x= Data_Quality_Description__c, y=n, fill = Converted)) +
geom_col(aes(group = 1), color = "black")


```

```{r echo=FALSE}
#df_total$Country <- ifelse(df_total$Country == "American Samoa" | df_total$Country == "CA" | df_total$Country == "Canada" |
#                            df_total$Country == "CANADA" )

#df_total_4 <- df_total %>% group_by(Country , Converted = as.factor(IsConverted)) %>%  dplyr::count(as.factor(IsConverted))

#df_total_4



#ggplot(df_total_3, aes(x= Data_Quality_Description__c, y=n, fill = Converted)) +
#geom_col(aes(group = 1), color = "black")


```




---
# Background Notes: The word customer left in the leads
* It is an intial communication between the customers and us
* We could get to know the customer more
* Get well prepared when we reach out to them
* Find potential rules behind the background notes

---
# Background Notes: Converted vs Non-Converted 


```{r}

df_total$Background_Notes__c <- ifelse(is.na(df_total$Background_Notes__c), "0", "1")

df_total_5 <- df_total %>% group_by(Background_Notes__c, Converted = as.factor(IsConverted)) %>%  dplyr::count(as.factor(IsConverted))


ggplot(df_total_5, aes(x= Background_Notes__c, y=n, fill = Converted)) +
geom_col(aes(group = 1), color = "black")

```




```{r echo=FALSE}


#drop na value

#df_total <- na.omit(df_total)

#summary(df_total)

```


```{r echo=FALSE}

#step1 <- step(glm(IsConverted ~ as.factor(Background_Notes__c)+Data_Quality_Description__c+Data_Quality_Score__c+LeadSource+Industr#y, data=df_total),direction="both")
   
```


```{r echo=FALSE}
#df_total


#lg1 <- glm(IsConverted ~ Data_Quality_Description__c + LeadSource + Industry, data=df_total)

#summary(lg1)

```




```{r echo=FALSE}
#####background notes, from the notes we got from the potential customers, we can get to know the customers better
## and we can gain experience their level of interest, so that the marketing team can better target them and adjust thier strategy to reach out to them 

#install.packages("tm")
library(tm)

docs <- Corpus(DirSource("C:/teporaryFiles/indi/note"))

inspect(docs)


##start processing
docs <- tm_map(docs, removePunctuation)
docs <- tm_map(docs, removeWords, c("\nNULL", "\n", "NULL", "the", "and", "for", "our", "have", "are", "with",
                                    "would", "you", "can", "your", "about", "that", "this", "how"))

tospace <- content_transformer(function(x, pattern) {return(gsub(pattern, "", x))})
docs <- tm_map(docs, tospace, "\n")


docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, content_transformer(tolower))




```


```{r echo=FALSE}


# Build a term-document matrix
docs1 <- TermDocumentMatrix(docs)
docs_m <- as.matrix(docs1)
# Sort by descearing value of frequency
docs_v <- sort(rowSums(docs_m),decreasing=TRUE)
docs_d <- data.frame(word = names(docs_v),freq=docs_v)
# Display the top 5 most frequent words
#head(docs_d, 10)



```

---
# word cloud: Frequent Words appear in the background notes

```{r echo=FALSE, fig.height=7, fig.width=10}

#install.packages("wordcloud")
library(wordcloud)

#generate word cloud
set.seed(1234)

wordcloud(words = docs_d$word, freq = docs_d$freq, min.freq = 5,
          max.words=100, random.order=FALSE, rot.per=0.40, 
          colors=brewer.pal(8, "Dark2"))

```


---
# Top Ten Most Frequent Words appear in Background Notes

```{r echo=FALSE, fig.height=6, fig.width=12}

# Plot the most frequent words
barplot(docs_d[1:10,]$freq, las = 2, names.arg = docs_d[1:10,]$word,
        col ="lightgreen", main ="Top 10 most frequent words",
        ylab = "BackgroundWord frequencies")


```



```{r echo=FALSE}
####contain specific words, the reason is that to if the customer leave specific words are more likely to be converted  as real customer

df_total <- rbind(Q3_2021, Q1_2021, Q3_2020, Q1_2020, Q3_2019, Q1_2019)


df_total$Industry <- ifelse (df_total$Industry == "Library", "Library", ifelse(df_total$Industry == "K-12 Education" ,"K-12 Education", ifelse(df_total$Industry == "Higher Education", "Higher Education", ifelse(df_total$Industry == "Other", "Other", "Profession"))))




####replace sample
df_total$Background_Notes__c <- ifelse(df_total$Background_Notes__c %like% "library", "library", ifelse(df_total$Background_Notes__c %like% "Library", "library", ifelse(df_total$Background_Notes__c %like% "overdrive", "overdrive", ifelse(df_total$Background_Notes__c %like% "OverDrive", "overdrive", ifelse(df_total$Background_Notes__c %like% "like", "like", ifelse(df_total$Background_Notes__c %like% "school", "school", ifelse(df_total$Background_Notes__c %like% "interest", "interest",  ifelse(df_total$Background_Notes__c %like% "public", "public",ifelse(df_total$Background_Notes__c %like% "books", "books", ifelse(df_total$Background_Notes__c %like% "information", "information", ifelse(df_total$Background_Notes__c %like% "access", "access", ifelse(df_total$Background_Notes__c %like% "thank","thank", "other"))))))))))))

#library(dplyr)

#df_total

###select rows
row1 <- df_total[df_total$Background_Notes__c %like% "library", ]
row2 <- df_total[df_total$Background_Notes__c %like% "overdrive", ]
row3 <- df_total[df_total$Background_Notes__c %like% "like", ]
row4 <- df_total[df_total$Background_Notes__c %like% "school", ]
row5 <- df_total[df_total$Background_Notes__c %like% "interest", ]
row6 <- df_total[df_total$Background_Notes__c %like% "other", ]
row7 <- df_total[is.na(df_total$Background_Notes__c), ]
row8 <- df_total[df_total$Background_Notes__c %like% "public", ]
row9 <- df_total[df_total$Background_Notes__c %like% "books", ]
row10 <- df_total[df_total$Background_Notes__c %like% "information", ]
row11 <- df_total[df_total$Background_Notes__c %like% "access", ]
row12 <- df_total[df_total$Background_Notes__c %like% "thank", ]

df_total7 <- rbind(row1, row2, row3, row4, row5, row8, row9, row10, row11, row12)
```



---
# Convertion Situation based on Background Key Words

```{r echo=FALSE, fig.height=6, fig.width=12}

###visual stuff

df_total_6 <- df_total7 %>% group_by(cohort, Background_Notes__c) %>% dplyr::summarise(TotalConverted = sum(IsConverted))



ggplot(df_total_6, aes(x=cohort, y=TotalConverted, fill = Background_Notes__c), group = 1) +
  geom_bar(stat = "identity", color="black")




###logistic or decrison trees model 


###


###how to track leads



```

```{r echo=FALSE}
#df_total7$IsConverted <- ifelse(df_total7$IsConverted == 1, "Yes", "No")

```


---
# Compare Convertion Situation based on Key Words
```{r echo=FALSE, fig.height=6, fig.width=12}
df_total7$Convertedornot <- ifelse(df_total7$IsConverted == 1, "Yes", "No")

df_total8 <- df_total7 %>% dplyr::group_by(Background_Notes__c, Convertedornot) %>% dplyr::count(Convertedornot)

#df_total8

ggplot(df_total8, aes(x=Background_Notes__c, y=n, fill = Convertedornot), group = 1) +
  geom_bar(stat = "identity", color="black")
```

---
# Comvertion Rate Based on Key words in Background Notes
# Top: thank, information, like, interest above 75%

```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}

df_total9 <- df_total7 %>% dplyr::group_by(Background_Notes__c) %>% dplyr::summarise(total=sum(as.numeric(IsConverted)))

df_total10 <- df_total7 %>% dplyr::group_by(Background_Notes__c) %>% dplyr::count(Background_Notes__c)

#df_total10

df_total11 <- df_total9
df_total11$ratio <- df_total9$total/df_total10$n * 100

#df_total11

ggplot(df_total11, aes(x=Background_Notes__c, y=ratio)) +
  geom_bar(stat = "identity", color = "black")
  

```


---
# Model: figure out factor influence on convertion 
* Only Industry and Data Quality Score are significant

```{r echo=FALSE, message=FALSE, warning=FALSE}

###logistic 
#lg1 <- glm(IsConverted ~ Data_Quality_Score__c + Industry + Background_Notes__c + LeadSource,df_total7, family = "binomial")

#summary(lg1)



```


---
# Decistion Tree
* Only Industry and Data Quality Score are significant
```{r echo=FALSE, fig.height=6, fig.width=12, warning=FALSE}


library(rpart)


#install.packages("rpart.plot")
library(rpart.plot)

#df_total7

df_total7_1 <- na.omit(df_total7)
df_total7_2 <- df_total7[, c("IsConverted", "Data_Quality_Score__c", "Industry", "Background_Notes__c", "LeadSource","Data_Quality_Description__c")]

df_total7_2

df_total7_2[, "IsConverted"] <- as.factor(df_total7_2[, "IsConverted"])
tree1 <- rpart(IsConverted ~ Industry + Background_Notes__c +LeadSource, data = df_total7_2, method = "class")

#tree1

rpart.plot(tree1)


```






