---
institute: "OverDrive"
output:
 xaringan::moon_reader:
    seal: FALSE
    includes: 
    css: ["default", "./my-theme.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
date: '2022-08-08'
---

layout: true

<div class="my-footer"><span> OverDrive Confidential: Internal Use Only
</span></div> 

---

class: center, middle


<br />
 <span style="color:white"> <font size="9">**RBD M&A**</span></font>
 <br />
 <span style="color:white"> <font size="6">** **</span></font>
 <br />
<font size="5">
August 8, 2022
</font>
<br />
<font size="5">
Susan Gross; Refreshed by Hao&Benen
</font>
<br />
<font size="5">
Business Systems & Analytics
</font>



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, comment = NA)
knitr::opts_knit$set(root.dir = "C:/teporaryFiles/rbd")
options(scipen = 999)
options(cache = TRUE)

```



```{r load packages, echo=FALSE, message=FALSE, warning=FALSE}

setwd("C:/teporaryFiles/rbd")
require(ggplot2); require(tidyr); library(plyr); require(dplyr); require(RODBC); require(kableExtra); require(pander); require(lubridate); require(cowplot); require(data.table); require(knitr);  require(gridExtra); require(openxlsx); require(scales);

```

---
# <font size = "6"> Purpose 

  * <font size = "6"> Compare the Magazine Pre-Migration, Post-Migration and current Value, how are we doing after the acquisition? </font> <br />
  * <font size = "6"> Magazine Convertion to other OverDrive product and Magazine only customers  </font> <br />
  * <font size = "6"> New Magazine Customer, are they here for the Magazine or brought to other OD products   </font> <br />
  * <font size = "6"> Lost Magazine Customer, how do we lost them, are they still stay for other OD product   </font> <br />


```{r loadthedata, echo=FALSE, message=FALSE, warning=FALSE}

cn <- odbcDriverConnect('driver={SQL Server};server=reportDB;database=master;trusted_connection=true')

  
df_2019 <- sqlQuery(cn,
                         paste("
 SELECT 
       [Account_18_Digit_ID__c]
      ,CAST([End_Date__c] AS DATE) AS [End_Date__c]
      ,[Simultanous_Use__c]
      ,CAST([Start_Date__c] AS DATE) AS [Start_Date__c]
      ,[Status__c]
      ,[Subscription_Name__c]
      ,[Total_Price_USD__c]
      ,[Unit_Count__c]
	  , Price_Per_Day = [Total_Price_USD__c]/DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST([End_Date__c] AS DATE))
	  , StartedDaysAgo = DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST(GETDATE() AS DATE)) 
	  , EndedDaysAgo = DATEDIFF(DAY, CAST([End_Date__c] AS DATE) , CAST(GETDATE() AS DATE)) 
	  , ActiveSubscriptionDays = DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST([End_Date__c] AS DATE)) 
	  , rbpc.Pre_Migration_Status__c
  FROM [sf_mirror].[dbo].[Product_Subscriptions__c] psbc
  left join sf_mirror.dbo.RBD_Historical_Product__c rbpc on rbpc.Account__c = psbc.Account_18_Digit_ID__c
  WHERE Format__c LIKE '%Magazine%'
  and Start_Date__c >= CONVERT(datetime, '2019-06-30')
  and Start_Date__c < CONVERT(datetime, '2020-06-30')
  --AND CR_ID__c IN ( 814, 612)
  AND Total_Price_USD__c >0
  ORDER BY  Account_18_Digit_ID__c
"))
  

df_2020 <- sqlQuery(cn, 
                    paste("
                              SELECT  --CR_ID__c
       [Account_18_Digit_ID__c]
      ,CAST([End_Date__c] AS DATE) AS [End_Date__c]
      ,[Simultanous_Use__c]
      ,CAST([Start_Date__c] AS DATE) AS [Start_Date__c]
      ,[Status__c]
      ,[Subscription_Name__c]
      ,[Total_Price_USD__c]
      ,[Unit_Count__c]
	  , Price_Per_Day = [Total_Price_USD__c]/DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST([End_Date__c] AS DATE))
	  , StartedDaysAgo = DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST(GETDATE() AS DATE)) 
	  , EndedDaysAgo = DATEDIFF(DAY, CAST([End_Date__c] AS DATE) , CAST(GETDATE() AS DATE)) 
	  , ActiveSubscriptionDays = DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST([End_Date__c] AS DATE)) 
	  , rbpc.Pre_Migration_Status__c
  FROM [sf_mirror].[dbo].[Product_Subscriptions__c] psbc
  left join sf_mirror.dbo.RBD_Historical_Product__c rbpc on rbpc.Account__c = psbc.Account_18_Digit_ID__c
  WHERE Format__c LIKE '%Magazine%'
  and Start_Date__c >= CONVERT(datetime, '2020-06-30')
  and Start_Date__c < CONVERT(datetime, '2021-06-30')
  --AND CR_ID__c IN ( 814, 612)
  AND Total_Price_USD__c >0
  ORDER BY  Account_18_Digit_ID__c
                          " ))


df_2021 <- sqlQuery(cn,
                    paste("
                           SELECT  --CR_ID__c
       [Account_18_Digit_ID__c]
      ,CAST([End_Date__c] AS DATE) AS [End_Date__c]
      ,[Simultanous_Use__c]
      ,CAST([Start_Date__c] AS DATE) AS [Start_Date__c]
      ,[Status__c]
      ,[Subscription_Name__c]
      ,[Total_Price_USD__c]
      ,[Unit_Count__c]
	  , Price_Per_Day = [Total_Price_USD__c]/DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST([End_Date__c] AS DATE))
	  , StartedDaysAgo = DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST(GETDATE() AS DATE)) 
	  , EndedDaysAgo = DATEDIFF(DAY, CAST([End_Date__c] AS DATE) , CAST(GETDATE() AS DATE)) 
	  , ActiveSubscriptionDays = DATEDIFF(DAY, CAST([Start_Date__c] AS DATE) , CAST([End_Date__c] AS DATE)) 
	  , rbpc.Pre_Migration_Status__c
  FROM [sf_mirror].[dbo].[Product_Subscriptions__c] psbc
  left join sf_mirror.dbo.RBD_Historical_Product__c rbpc on rbpc.Account__c = psbc.Account_18_Digit_ID__c
  WHERE Format__c LIKE '%Magazine%'
  and Start_Date__c >= CONVERT(datetime, '2021-06-30')
  and Start_Date__c < CONVERT(datetime, '2022-06-30')
  --AND CR_ID__c IN ( 814, 612)
  AND Total_Price_USD__c >0
  ORDER BY  Account_18_Digit_ID__c
                          "))



df_2019$year <- 2019
#head(df_2019)

df_2020$year <- 2020

df_2021$year <- 2021

df_all <- rbind(df_2019, df_2020, df_2021)

```



---
# <font size = "5">Account Level in ProductSubscription Table, Total Revenue in Account Level
# <font size = "4"> Constantly Growing 


```{r revenue1, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}
df_dall<-df_all %>% group_by(year)%>% dplyr::summarise(TotalSpend=sum(Total_Price_USD__c))


ggplot(df_dall, aes_string(x = "year", y="TotalSpend")) +   geom_bar(stat = "identity", color="black") +theme_classic(base_size=15)+ theme(legend.title= element_blank()) + labs( y = "Spend in $", x = "year")+ scale_y_continuous(labels = scales::comma)+scale_fill_manual(values=c( "#7fb1c8","#0A2240","#a3f896"))
```

---
#<font size = "6"> New to Overdrive/Exsiting Customer/Unknown

```{r revenue2, echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.width=12}
df_all1 <- df_all

for(i in 1:length(df_all$Account_18_Digit_ID__c)) {
   if(is.na(df_all1[i, 'Pre_Migration_Status__c'])) {
     df_all1[i, 'Pre_Migration_Status__c'] <- 'Unknown'
   }
}


df_dall1<-df_all1 %>% group_by(year, Pre_Migration_Status__c)%>% dplyr::summarise(TotalSpend=sum(Total_Price_USD__c))


ggplot(df_dall1, aes_string(x = "year", y="TotalSpend", fill="Pre_Migration_Status__c" )) +   geom_bar(stat = "identity", color="black") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")
```



```{r dataload2, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}

## dc levels
dc_2021 <- read.csv("2021st.csv")
dc_2020 <- read.csv("2020st.csv")
dc_2019 <- read.csv("2019st.csv")

alld2021 <- read.csv("2021all.csv") 

#head(alld2021)
alld2020 <- read.csv("2020all.csv")
#head(alld2020)

#dc_2021

```

```{r dataprocess1, echo=FALSE, message=FALSE, warning=FALSE}

dc_2019$year <- 2019
dc_2020$year <- 2020
dc_2021$year <- 2021
dc_all <- rbind(dc_2019, dc_2020, dc_2021)

dc_all$Market <- ifelse(dc_all$Platform =="DLR" & dc_all$Region =="Americas", "NAPL", ifelse(dc_all$Platform == "SDL" & dc_all$Region == "Americas", "K12NA", ifelse(dc_all$Platform == "DLR" & dc_all$Region != "Americas", "GL&E", "Professional")))
#dc_all
```

---
#<font size = "5"> Digital Collection Level, Total Magazine Revenue
#<font size = "4"> Compare with Account level, there's slightly difference in 2020, Data missing during the migration process
```{r revenue3, echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.width=12}
##yearly distribution


dc_all %>% group_by(year)%>% dplyr::summarise(Totalspend=sum(TotalSpend)) %>% 
ggplot(aes(x = year, y=Totalspend)) + geom_bar(stat = "identity", color="black") + theme_classic(base_size=15) + theme(legend.title= element_blank()) + labs( y = "Spend in $", x = "year")+ scale_y_continuous(labels = scales::comma)+scale_fill_manual(values=c( "#7fb1c8","#0A2240","#a3f896"))


```




---
#<font size = "6"> DC Level Revenue based on Market 

```{r revenue4, echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.width=12}
###platform, region, 

dc_all1 <- dc_all %>% group_by(year, Market)%>% dplyr::summarise(TotalSpend=sum(TotalSpend))

#dc_all1

ggplot(dc_all1, aes(x = year, y= TotalSpend, fill=Market)) +   
geom_bar(stat = "identity", color="black") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + 
labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")

```

---
# <font size = "6">DC Level Revenue based on Region
# <font size = "4">Americas always the largest part, while Europe and Oceania grow fast

```{r revenue5, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=12}


dc_all2 <- dc_all %>% group_by(year, Region)%>% dplyr::summarise(TotalSpend=sum(TotalSpend))

#dc_all2

ggplot(dc_all2, aes(x = year, y= TotalSpend, fill=Region)) +   
geom_bar(stat = "identity", color="black") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + 
labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")


```

---
# <font size = "6"> Active Account Percentage
 
```{r echo=FALSE, fig.height=5, fig.width=10, message=FALSE, warning=FALSE}

dc_all_active <- subset(dc_all, dc_all$TotalSpend > 0)


dc_all_active19 <- subset(dc_all_active, dc_all_active$year == 2019)
dc_all_active20 <- subset(dc_all_active, dc_all_active$year == 2020)
dc_all_active21 <- subset(dc_all_active, dc_all_active$year == 2021)





dc_all_active <- data.frame( no = c(2019,2020,2021),
                             active = c(length(dc_all_active19$CRID)/length(dc_2019$CRID), length(dc_all_active20$CRID)/length(dc_2020$CRID), length(dc_all_active21$CRID)/length(dc_2021$CRID))
)



ggplot(dc_all_active, aes(x=no, y=active)) + 
  geom_bar(stat = "identity", color="black", fill="#4f8e9c") + 
  theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "Active", x = "Year")+scale_fill_manual(values=c( "#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")
  

```




---
# <font size = "6"> Americas Region Revenue based on Subregion

```{r revenue6, echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.width=12}

##subregion 

dc_all3 <- dc_all %>% mutate(Region="Americas")  %>% group_by(year, Territory)%>% dplyr::summarise(TotalSpend=sum(TotalSpend))

#dc_all3

#ggplot(dc_all3, aes(x = year, y= TotalSpend, fill=Territory)) +   
#geom_bar(stat = "identity", color="black") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + 
#labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", #"#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")


ggplot(data=dc_all3, aes(x=year, y=TotalSpend, group=Territory)) +
  geom_line(aes(color = Territory))+
  geom_point() +
  theme(legend.title = element_blank(), axis.title = element_text(size = 16), axis.text = element_text(size = 14), legend.text = element_text(size = 16))



```

---
# <font size = "6"> Revenue based on subscription tire

```{r revenue10, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6, fig.width=12}
###subscription tire

dc_all4 <- dc_all %>%  group_by(year, tire = as.factor(Subscription_Tire))%>% dplyr::summarise(TotalSpend=sum(TotalSpend))


ggplot(data=dc_all4, aes(x=year, y=TotalSpend, group=tire)) +
  geom_line(aes(color = tire)) +
  geom_point(aes(color = tire))



```




```{r convert1, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}
#### transformation 

dc_all$transfrom <- 0

dc_all <- dc_all %>% replace(.=="NULL", NA)
  
for(i in 1:length(dc_all$CPC)) {
  if(is.na(dc_all[i, "CPC"])) {
    dc_all[i, "CPC"] <- 0
  }
}


for(i in 1:length(dc_all$PurchaseOrders)) {
  if(is.na(dc_all[i, "PurchaseOrders"])) {
    dc_all[i, "PurchaseOrders"] <- 0
  }
}


for(i in 1:length(dc_all$otherSub)) {
  if(is.na(dc_all[i, "otherSub"])) {
    dc_all[i, "otherSub"] <- 0
  }
}



dc_all$transfrom <-ifelse (dc_all$CPC > 0 | dc_all$PurchaseOrders > 0 | dc_all$otherSub > 0, "1", "0")

dc_all$transformCPC <- ifelse(dc_all$CPC > 0, "1", "0")

dc_all$transformPO <- ifelse(dc_all$PurchaseOrders > 0, "1", "0")

dc_all$transformOther <- ifelse(dc_all$otherSub > 0, "1", "0")

#dc_all
```



```{r convert2, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}

###would be better to use content e-book, audio-book 


dc_all5<- dc_all 

dc_all5$count <- 1

dc_all5 <- dc_all5 %>% group_by(year)%>% dplyr::summarise(Total=sum(count), Overall=sum(as.numeric(transfrom)), CPC = sum(as.numeric(transformCPC)), PurchaseOrder=sum(as.numeric(transformPO)), otherSub = sum(as.numeric(transformOther))) 

#dc_all5


#ggplot(dc_all5, aes(x = year, y=Total)) 
#+ geom_col(stat = "identity", color="black", fill="Total") 
#+ theme_classic(base_size=15) + theme(legend.title= element_blank()) + labs( y = "Spend in $", x = "year")+ #scale_y_continuous(labels = scales::comma)+scale_fill_manual(values=c( "#7fb1c8","#0A2240","#a3f896"))


```


---
class: inverse, left, middle
<br /><br />
<h2> Magazine Customers Also Purchase other OD products </h2> 




---
# <font size = "6"> Convertion Volume
```{r convert3, echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.width=12}

###transform plot
ggplot(dc_all5, aes(x=year)) + 
  geom_col(aes( y = Total), size = 1, color = "black", fill = "cadetblue1") +
  geom_line(aes(y = Overall, color = "Overall"), size = 1) + 
  geom_line(aes( y = CPC, color = "CPC"), size = 1) + 
  geom_line(aes( y = PurchaseOrder, color = "PurchaseOrder"), size = 1) +
  geom_line(aes( y = otherSub, color = "otherSub"), size = 1) +
  scale_color_manual(values = c("red", "aquamarine4", "yellow", "darkmagenta"))

```


---
#<font size = "6"> Convertion Percentage 

```{r convert4, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}

dc_all6 <- dc_all5 %>% dplyr::summarise(year=year, "Overall in %"=Overall/Total * 100, "CPC in %"=CPC/Total * 100, "PurchaseOrder in %" = PurchaseOrder/Total * 100, "otherSub in %" = otherSub/Total * 100)

dc_all6

```


---
#<font size = "6"> Convertion Percentage in Each Category

```{r convert5, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}


ggplot(data = dc_all6 %>% gather(Categories, Percentage, -year), 
       aes(x = year, y = Percentage, fill = Categories)) + 
    geom_bar(stat = 'identity', position = 'dodge')


```



---
# <font size = "6"> Convention Volumn Compare Based on Platform

```{r convert6, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}


#### there're around 9%-10% customers, they only purchase maginze,   what do they have in common?   
#### what's difference in                          visulize and modeling


dc_all7 <- dc_all %>% filter(transfrom == 0)
#dc_all7   ###non transform at all, only magazine.

#summary(dc_all7)

###sample of other service
### weighten the data

dc_all8 <- dc_all %>% filter(transfrom == 1)

dc_all8 <- dc_all8[sample(nrow(dc_all8), 142), ]

#dc_all8


#### combine dataset
dc_all9 <- rbind(dc_all7, dc_all8)



##compare count
dc_all9_1 <- dc_all9 %>% group_by(Platform, transfrom) %>% count(transfrom) 

#dc_all9_1

ggplot(dc_all9_1, aes(x=Platform, y=n, fill = transfrom))  + geom_bar(stat="identity", color="black")


###compare spend 
####drop the order dc, focus on the new dcs? 
#### for the new comers, are they drawed by the RBD, existed or transformed from other part? 


```




---
# <font size = "6"> Convertion and Non-Convertion Customer Spend Compare
```{r convert7, echo=FALSE, message=FALSE, warning=FALSE, fig.height=4, fig.width=11}
       

dc_all9 %>% group_by(Platform, transfrom) %>% dplyr::summarise(Sum = sum(TotalSpend)) %>% 
  ggplot(aes(x=Platform, y=Sum, fill=transfrom)) + geom_bar(stat = "identity")

###transformed are more generous 

```

```{r convert8, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}
#dc_all9


dc_all9_2 <- subset(dc_all, dc_all9$Monthly_Spend_Goal < 500000)

dc_all9_3 <- subset(dc_all9_2,  as.numeric(dc_all9_2$Days_Live) < 7000 & as.numeric(dc_all9_2$Days_Live) >400)

ltrans <- glm(as.factor(transfrom) ~ Subscription_Tire + Region +as.numeric(Days_Live) + as.numeric(Monthly_Spend_Goal) + Platform + Market, data = dc_all9, family = "binomial")

#summary(ltrans)
```


---

# <font size = "6"> Model Prepare, Outlier Dection
# <font size = "4"> Drop monthly goal above 500000, days live above 7000 or below 400
```{r echo=FALSE, fig.height=5, fig.width=12}

box1 <- boxplot(dc_all9$Monthly_Spend_Goal)
###drop monthly goal above 500000

box2 <- boxplot(as.numeric(dc_all9$Days_Live))
###drop days live about 7000 or below 400

#gridExtra::grid.arrange(box1, box2)
```

---
# <font size = "6"> Model 1
```{r echo=FALSE, fig.height=5, fig.width=12, message=FALSE, warning=FALSE}

ltrans1 <- glm(as.factor(transfrom) ~ Subscription_Tire + Region +as.numeric(Days_Live) + as.numeric(Monthly_Spend_Goal) + Platform + Market, data = dc_all9_3, family = "binomial")

summary(ltrans1)

```


```{r convert9, echo=FALSE, message=FALSE, warning=FALSE}

####new comer or lost
### for new comer, explore are they attricted here for magazine or transformed from other overdrive products
### for the lost, are they still with us in other products? 
dc_2020new <- subset(dc_2020, !(CRID %in% dc_2019$CRID))
dc_2020new
dc_2020lost <- subset(dc_2019, !(CRID %in% dc_2020$CRID))
#dc_2020lost
dc_2021new <- subset(dc_2021, !(CRID %in% dc_2020$CRID))
#dc_2021new
dc_2021lost <- subset(dc_2020, !(CRID %in% dc_2021$CRID))
#dc_2021lost
```

```{r convert10, echo=FALSE, message=FALSE, warning=FALSE}

dc_2020new_1 <- dc_2020new %>% group_by(Platform) %>% dplyr::count(Platform) 

#onlym2020_1

dc_2021new_1 <- dc_2021new %>% group_by(Platform) %>% dplyr::count(Platform)

#onlym2021_1

ggplot() +
  geom_line(data = dc_2020new_1, aes(x=Platform, y=n, group = 1), color = "red") +
  geom_line(data = dc_2021new_1, aes(x=Platform, y=n, group =2), color = "blue")




```



```{r dataprocess3, echo=FALSE, message=FALSE, warning=FALSE}

onlym2020 <- subset(dc_2020new, !(CRID %in% alld2020$CRID))

#onlym2020
###42 out of 350 of new comer here just for the magazine, implied 308 of them brought by other od service

onlym2021 <- subset(dc_2021new, !(CRID %in% alld2021$CRID))

#onlym2021
##85 out of 720 of the new comer here just for the magazine, implied 635 of them transformed from other od service 
```



---
# <font size = "6"> New customers that only come for Magazine 2020vs2021
# <font size = "6"> 2020vs2021
```{r new1, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}
onlym2020_1 <- onlym2020 %>% group_by(Platform) %>% count(Platform) 

#onlym2020_1

onlym2021_1 <- onlym2021 %>% group_by(Platform) %>% count(Platform)

#onlym2021_1

ggplot() +
  geom_line(data = onlym2020_1, aes(x=Platform, y=n, group = 1), color = "2020") +
  geom_line(data = onlym2021_1, aes(x=Platform, y=n, group =2), color = "2021") +
   scale_color_manual(values = c("aquamarine4","darkmagenta")) +
    labs( y = "New DCs", x = "Platform")
#  geom_point(data = data1, aes(x = clarity, y = m), color = "blue") + # must include argument label "data"
#  geom_point(data = data2, aes(x = clarity, y = m))
```


---
# <font size = "6"> New customers Spend, only for Magazine 
# <font size = "6"> 2020 Spend, only for Magazine 

```{r new2, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5, fig.width=12}
only2020_2 <- onlym2020 %>% group_by(Platform) %>% dplyr::summarise(TotalSpend = sum(TotalSpend))
#only2020_2
only2021_2 <- onlym2021 %>% group_by(Platform) %>% dplyr::summarise(TotalSpend = sum(TotalSpend))
#only2021_2
 ggplot() +
geom_col(data = only2020_2, aes(x=Platform, y=TotalSpend), fill = "#8EC549")



```

---
# <font size = "6"> New customers Spend, only for Magazine 
# <font size = "6"> 2021 Spend, only for Magazine 


```{r echo=FALSE, fig.height=5, fig.width=12}

ggplot() +
geom_col(data = only2021_2, aes(x=Platform, y=TotalSpend), fill = "#8EC549")

```




---
<br /><br />
# <font size = "6"> Magazine Lost Customers
# <font size = "6"> 2020: 13 out of 13 still with us, they just cancel the magazine subscription
# <font size = "6"> 2021: 22 out of 26 still with us, 4 of them not with us at all.
```{r lost1, echo=FALSE, message=FALSE, warning=FALSE}
stil2020_1 <- subset(dc_2020lost, CRID %in% alld2020$CRID)
#stil2020_1
###13 out of 13 still with us, they just cancel the magazine subscription
stil2021_1 <- subset(dc_2021lost, CRID %in% alld2021$CRID)

alllost <- subset(dc_2021lost, !(CRID %in% stil2021_1$CRID))
#alllost
###22 out of 26 still with us, 4 of them not with us at all.

```

---
# <font size = "6"> Completely lost customers: 12748 12779 13038 2312
# <font size = "6"> 12748: Izmir Institute of High Technology (TR)     1
# <font size = "6"> 12779: Thunder Bay Public Library (CA)             3
# <font size = "6"> 13038	: MBSA Majlis Bandaraya Shah Alam (MY)       1
# <font size = "6"> 2312: York Public Library (ME)                     1






---
# Appendix
#<font size = "6"> Account Level in Content Metrics
# <font size = "6"> Exsiting and New Customers
```{r echo=FALSE, fig.height=5, fig.width=12}

cn1 <- odbcDriverConnect('driver={SQL Server};server=reportDB;database=sf_mirror;trusted_connection=true')

ct1 <- sqlQuery(cn1,
                    paste("
SELECT DISTINCT rhp.Account__c
, Migration_Date__c = CAST(rhp.Migration_Date__c AS DATE)
, rhp.Pre_Migration_Status__c
,	cm.Account_Name__c
	, cm.Format_Class__c
   ,Time_Frame =
	   CASE WHEN  cm.Month__c IN ('July','August', 'September', 'October', 'November', 'December') AND Year__c = 2020 THEN 'Post-acquisition'
		 WHEN  cm.Month__c IN ('January', 'February','March', 'April', 'May', 'June') AND Year__c = 2020 THEN 'Pre-acquisition'	
		 WHEN  cm.Month__c IN('January', 'February','March', 'April', 'May', 'June')   AND Year__c = 2022 THEN 'Current'   END
	, Total_Spend = SUM(cm.Total_Monthly_Content_Spend__c)
FROM  sf_mirror.dbo.RBD_Historical_Product__c rhp
LEFT JOIN sf_mirror.dbo.Content_Metrics__c cm ON rhp.Account__c = cm.Account_Name__c
WHERE Format_Class__c like '%Magazine%'
AND (cm.Year__c = 2020 OR cm.Year__c = 2022)
GROUP BY  rhp.Account__c
, CAST(rhp.Migration_Date__c AS DATE)
, rhp.Pre_Migration_Status__c
, cm.Account_Name__c
	, cm.Format_Class__c
   ,   CASE WHEN  cm.Month__c IN ('July','August', 'September', 'October', 'November', 'December') AND Year__c = 2020 THEN 'Post-acquisition'
		 WHEN  cm.Month__c IN ('January', 'February','March', 'April', 'May', 'June') AND Year__c = 2020 THEN 'Pre-acquisition'	
		 WHEN  cm.Month__c IN('January', 'February','March', 'April', 'May', 'June')   AND Year__c = 2022 THEN 'Current' END
ORDER BY cm.Account_Name__c

                          "))

# head(ct1)

# na.omit(ct1)

#ct1 <- na.omit(ct1$Time_Frame)
#ct1
```



```{r echo=FALSE, fig.height=5, fig.width=12}

ct3 <- ct1 %>% dplyr::group_by(Time_Frame, Pre_Migration_Status__c)%>% dplyr::summarise(TotalSpend=sum(Total_Spend),)


ggplot(ct3, aes_string(x = "Time_Frame", y="TotalSpend", fill="Pre_Migration_Status__c" )) +   geom_bar(stat = "identity", color="black") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")




```


```{r echo=FALSE, fig.height=5, fig.width=12}

cn1 <- odbcDriverConnect('driver={SQL Server};server=reportDB;database=sf_mirror;trusted_connection=true')

ct4_1 <- sqlQuery(cn1,
                    paste("
select Account_Name__c,
TotalSpend = Sum(Total_Monthly_Content_Spend__c),
TotalUnits = Sum(Total_Monthly_Units__c)
 ,Time_Frame =
	   CASE WHEN  Month__c IN ('July','August', 'September', 'October', 'November', 'December') AND Year__c = 2020 THEN 'Post-acquisition'
		 WHEN  Month__c IN ('January', 'February','March', 'April', 'May', 'June') AND Year__c = 2020 THEN 'Pre-acquisition'	
		 WHEN  Month__c IN('January', 'February','March', 'April', 'May', 'June')   AND Year__c = 2022 THEN 'Current'   END
from sf_mirror.dbo.Content_Metrics__c
where Format_Class__c like '%magazine%'
AND (Year__c = 2020 OR Year__c = 2022)
Group BY Account_Name__c,
CASE WHEN  Month__c IN ('July','August', 'September', 'October', 'November', 'December') AND Year__c = 2020 THEN 'Post-acquisition'
		 WHEN  Month__c IN ('January', 'February','March', 'April', 'May', 'June') AND Year__c = 2020 THEN 'Pre-acquisition'	
		 WHEN  Month__c IN('January', 'February','March', 'April', 'May', 'June')   AND Year__c = 2022 THEN 'Current'   END

                          "))


ct4_1 <- na.omit(ct4_1)
```


```{r echo=FALSE}
cn1 <- odbcDriverConnect('driver={SQL Server};server=reportDB;database=sf_mirror;trusted_connection=true')

ct4_2 <- sqlQuery(cn1,
                    paste("
select Account_Name__c,
TotalSpend = Sum(Total_Monthly_Content_Spend__c),
TotalUnits = Sum(Total_Monthly_Units__c)
 ,Time_Frame =
	   CASE WHEN  Month__c IN ('July','August', 'September', 'October', 'November', 'December') AND Year__c = 2020 THEN 'Post-acquisition'
		 WHEN  Month__c IN ('January', 'February','March', 'April', 'May', 'June') AND Year__c = 2020 THEN 'Pre-acquisition'	
		 WHEN  Month__c IN('January', 'February','March', 'April', 'May', 'June')   AND Year__c = 2022 THEN 'Current'   END
from sf_mirror.dbo.Content_Metrics__c
where (Format_Class__c like '%eBook%' or Format_Class__c like '%Audiobook%')
AND (Year__c = 2020 OR Year__c = 2022)
Group BY Account_Name__c,
CASE WHEN  Month__c IN ('July','August', 'September', 'October', 'November', 'December') AND Year__c = 2020 THEN 'Post-acquisition'
		 WHEN  Month__c IN ('January', 'February','March', 'April', 'May', 'June') AND Year__c = 2020 THEN 'Pre-acquisition'	
		 WHEN  Month__c IN('January', 'February','March', 'April', 'May', 'June')   AND Year__c = 2022 THEN 'Current'   END

                          "))

ct4_2 <- na.omit(ct4_2)


```





---
# <font size = "6"> Magazine Spend VS Ebook&Audiobook Spend
# <font size = "6"> Magazine Spend

```{r echo=FALSE, fig.height=5, fig.width=12}
ct5_1 <-ct4_1 %>% group_by(Time_Frame) %>% dplyr::summarise(TotalSpend=sum(TotalSpend))


ggplot(ct5_1, aes_string(x = "Time_Frame", y="TotalSpend")) +   geom_bar(stat = "identity", color="black", fill = "#7fb1c8") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")


```


---
# <font size = "6"> Magazine Spend VS Ebook&Audiobook Spend
# <font size = "6"> Ebook&Audiobook Spend


```{r echo=FALSE}

ct5_2 <-ct4_2 %>% group_by(Time_Frame) %>% dplyr::summarise(TotalSpend=sum(TotalSpend))


ggplot(ct5_2, aes_string(x = "Time_Frame", y="TotalSpend")) +   geom_bar(stat = "identity", color="black", fill = "#A7A9AC") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")
```



```{r echo=FALSE}
###compare ct1 and ct6

ct4_1$convert <- "No"


for (i in 1:length(ct4_1$Account_Name__c)) {
  if(any(ct4_1$Account_Name__c==ct4_2[i, "Account_Name__c"])){
    ct4_1[i, "convert"] = "Yes"
  } else {
    ct4_1[i, "convert"] = "No"
  }
}

#ct4_1

```

---
# <font size = "6"> Magazine's Conversion to Ebook/Audiobook
# <font size = "6"> Number of account 

```{r echo=FALSE, fig.height=6, fig.width=12}


ct7_1 <- ct4_1 %>% group_by(Time_Frame, convert) %>% dplyr::count(convert)

#ct7_1

ggplot(ct7_1, aes_string(x = "Time_Frame", y="n", fill="convert" )) +   geom_bar(stat = "identity", color="black") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "Total", x = "Time")+scale_fill_manual(values=c( "#7fb1c8","#f8b996","#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")



```

---
# <font size = "6"> Magazine's Conversion to Ebook/Audiobook
# <font size = "6"> Total Spend 


```{r echo=FALSE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}


ct6_1 <-ct4_1 %>% group_by(Time_Frame, convert)%>% dplyr::summarise(TotalSpend=sum(TotalSpend))


ggplot(ct6_1, aes_string(x = "Time_Frame", y="TotalSpend", fill="convert" )) +   geom_bar(stat = "identity", color="black") +theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "TotalSpend", x = "year")+scale_fill_manual(values=c(  "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")



```

---
# <font size = "6"> Retention Rate
# <font size = "6"> Current VS POST

```{r echo=FALSE, fig.height=6, fig.width=12}
###magazine retention in Account level

ct4_1_pre <- subset(ct4_1, ct4_1$Time_Frame =="Pre-acquisition")
ct4_1_pos <- subset(ct4_1, ct4_1$Time_Frame =="Post-acquisition")
ct4_1_cur <- subset(ct4_1, ct4_1$Time_Frame =="Current")

ct4_1pos1 <- subset(ct4_1_pre, (ct4_1_pre$Account_Name__c %in% ct4_1_pos$Account_Name__c))
ct4_1cur1 <- subset(ct4_1_pos, (ct4_1_pos$Account_Name__c %in% ct4_1_cur$Account_Name__c))



ct4_retention <- data.frame( no = c("Post","Current"),
                             retention = c(length(ct4_1pos1$Time_Frame)/length(ct4_1_pre$Time_Frame), length(ct4_1cur1$Time_Frame)/length(ct4_1_pos$Time_Frame))
)



ggplot(ct4_retention, aes(x=no, y=retention)) + 
  geom_bar(stat = "identity", color="black", fill="#4f8e9c") + 
  theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "Retention Rate", x = "Time")+scale_fill_manual(values=c( "#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")
  

```


---
# <font size = "6"> Activity Rate
# Activity Rate in account level is pretty low

```{r echo=FALSE, fig.height=6, fig.width=12}
###magazine retention in Account level

ct4_1_preA <- subset(ct4_1_pre, ct4_1_pre$TotalSpend >0)
ct4_1_posA <- subset(ct4_1_pos, ct4_1_pos$TotalSpend >0)
ct4_1_curA <- subset(ct4_1_cur, ct4_1_cur$TotalSpend >0)


ct4_1pos1 <- subset(ct4_1_pre, (ct4_1_pre$Account_Name__c %in% ct4_1_pos$Account_Name__c))
ct4_1cur1 <- subset(ct4_1_pos, (ct4_1_pos$Account_Name__c %in% ct4_1_cur$Account_Name__c))



ct4_activity <- data.frame( no = c("Pre", "Post","Current"),
                             active = c(length(ct4_1_preA$Time_Frame)/length(ct4_1_pre$Time_Frame),length(ct4_1_posA$Time_Frame)/length(ct4_1_pos$Time_Frame), length(ct4_1_curA$Time_Frame)/length(ct4_1_cur$Time_Frame))
)



ggplot(ct4_activity, aes(x=no, y=active)) + 
  geom_bar(stat = "identity", color="black", fill="#4f8e9c") + 
  theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "Active Rate", x = "Time")+scale_fill_manual(values=c( "#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")
  

```



---
# <font size = "6"> New Comers
# <font size = "6"> Current VS POST
# Current is new comer for 2 years

```{r echo=FALSE, fig.height=6, fig.width=12}
ct4_1new1 <- subset(ct4_1_pos, !(ct4_1_pos$Account_Name__c %in% ct4_1_pre$Account_Name__c))

ct4_1new2 <- subset(ct4_1_cur, !(ct4_1_cur$Account_Name__c %in% ct4_1_pos$Account_Name__c))


ct4_newcomer <- data.frame( no = c("Post","Current"),
                             new = c(length(ct4_1new1$Time_Frame), length(ct4_1new2$Time_Frame))
)



ggplot(ct4_newcomer, aes(x=no, y=new)) + 
  geom_bar(stat = "identity", color="black", fill="#507f94") +
   theme_classic(base_size=20)+ theme(legend.title= element_blank()) + labs( y = "New Comer", x = "Time")+scale_fill_manual(values=c( "#a3f896","#A7A9AC", "#EE523B", "#231F20", "#507f94", "#8f3122", "#4f8e9c"))+ scale_y_continuous(labels = scales::comma)+ theme(legend.position="bottom")

```

